Results Text

### 2023-07-20 Charuco_DLT/rearrange_point_for_easywand.Rmd
Adding more calibrations

Fill in the name of the output CSV file from `detect_charuco.ipynb`.
```{r}
detections <- read_csv("/Users/Ben/Desktop/Charuco_DLT/charuco_boards/2023_02_09/boards.csv") |> 
  select(-`...1`)
```

Fill in the directory that has the video files and the names of each video.
```{r}
videodir <- '/Users/Ben/Desktop/Charuco_DLT/charuco_boards/2023_02_09'
camfiles <- c('checkerboard_V1.mp4','checkerboard_V2.mp4')
camfiles <- map(camfiles, ~ file.path(videodir, .x))
```

@@

And save out the CSV.
```{r}
write_csv(ptsforeasywand, "/Users/Ben/Desktop/Charuco_DLT/2023_02_XX_calibrationcharuco_xypts.csv")
```

>>>>

Fill in the name of the output CSV file from `detect_charuco.ipynb`.
```{r}
detections <- read_csv("/Users/Ben/Desktop/Fish-Midline-Processer/Charuco_DLT/charuco_boards/2023_06_29/boards.csv") |> 
  select(-`...1`)
```

Fill in the directory that has the video files and the names of each video.
```{r}
videodir <- '//Users/Ben/Desktop/Fish-Midline-Processer/Charuco_DLT/charuco_boards/2023_06_29'
camfiles <- c('checkerboard_V1.mp4','checkerboard_V2.mp4')
camfiles <- map(camfiles, ~ file.path(videodir, .x))
```

@@

And save out the CSV.
```{r}
write_csv(ptsforeasywand, "//Users/Ben/Desktop/Fish-Midline-Processer/Charuco_DLT/charuco_boards/2023_06_29/2023_06_29_calibrationcharuco_xypts.csv")
```

### 2023-07-20 Fish Data Analysis/Heading Cross Corr.qmd
Adding more calibrations

```{r}
library(gsignal)
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)
library(zoo)

@@

@@

Testing optimization
```{r}

x <- seq(0,2*pi,pi/10)
y1 <- sin(x)
y2 <- sin(x+pi/2 + rnorm(20,0,pi/4))

tester_window_size <- 5

y1_embed <- embed(y1,tester_window_size)
y2_embed <- embed(y2,tester_window_size)

list_embed <- data.frame(y1 = y1,y2 = y2)

cor_vals <- rollapply(list_embed, width = tester_window_size,
                      FUN = function(w) cor(list_embed[,1], list_embed[,2], method = "pearson", use = "complete.obs"),
                      align = "right")

cor_vals

z2 <- zoo(rnorm(6))
z2
rollapply(1:6, 3, mean)

Okay so now a specific correlation version

```{r}
get_corrs_lags_ben <- function(f1_data, f2_data){

  saved_ccf <- windowed_correlation_finder(f1_data,f2_data)

  corrs <- saved_ccf$ccf
  lags <- saved_ccf$lags

  return(list(output_corrs,output_lags))
}
```

@@

@@

ggplot(raw_heading_corrs_graphing %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = corrs,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_jitter(height = 0, alpha = 0.2)+
  #stat_dots(side = "both", binwidth = unit(dot_binwidth/2, "npc")) +
  geom_point(aes(y = Mean_Corr), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Corr-SD_Corr, ymax=Mean_Corr+SD_Corr), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("Max Correlation") +
  theme_light()+ 
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

>>>>

```{r}
library(gsignal)
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)
library(zoo)
library(viridis)

@@

# Bigger data

@@

@@

# Raw Data processing

@@

ggplot(raw_heading_corrs_graphing %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = corrs,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_jitter(height = 0, alpha = 0.2)+
  #stat_dots(side = "both", binwidth = unit(dot_binwidth/2, "npc")) +
  geom_point(aes(y = Mean_Corr), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Corr-SD_Corr, ymax=Mean_Corr+SD_Corr), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("Max Correlation") +
  theme_light()+ 
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

ggplot(raw_heading_corrs_sum %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = max_corr,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  #geom_jitter(height = 0, alpha = 0.2)+
  stat_dots(side = "both", binwidth = unit(dot_binwidth/2, "npc")) +
  geom_point(aes(y = Mean_Max_Corr), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Max_Corr-SD_Max_Corr, ymax=Mean_Max_Corr+SD_Max_Corr), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("Max Correlation") +
  theme_light()+ 
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

max_corr_glmer <- lmer(max_corr ~ Ablation + Darkness + (1|Data_ID), data = raw_heading_corrs_sum %>% filter(Flow == "Still Water"))
summary(max_corr_glmer)
Anova(max_corr_glmer)

@@

countour_lag_data <- raw_heading_corrs_graphing %>% mutate(round_corrs = round_any(corrs, 0.25),
                                                           round_dists = round_any(Distance, 2))

ggplot(countour_lag_data %>% filter(Flow == "Still Water" & Darkness == "Dark"),
       aes(x = Distance, y = corrs, color = lags))+
  geom_point()+
  scale_color_viridis()+
  theme_classic()

ggplot(countour_lag_data %>% filter(Flow == "Still Water" & Darkness == "Dark"),
       aes(x = Distance, y = lags))+
  geom_point()+
  theme_classic()

ggplot(countour_lag_data %>% filter(Flow == "Still Water" & Darkness == "Dark"),
       aes(x = corrs, y = lags))+
  geom_point()+
  theme_classic()

### 2023-07-20 Fish Data Analysis/Paper_Figures.qmd
Adding more calibrations

  new_autocorrs <- school_data_no_removals %>% group_by(Date_Trial) %>%
                    filter(!Date_Trial %in% c("2021_3_25_30","2020_7_28_29")) %>%
                    summarise(nnd_corr = abs(cor.test(NND, lag(NND, n = i))$estimate),
                              nnd_p = cor.test(NND, lag(NND, n = i))$p.value,
                              polar_corr = abs(cor.test(School_Polar, lag(School_Polar, n = i))$estimate),
                              polar_p = cor.test(School_Polar, lag(School_Polar, n = i))$p.value,
                              speed_corr = abs(cor.test(School_Speed, lag(School_Speed, n = i))$estimate),
                              speed_p = cor.test(School_Speed, lag(School_Speed, n = i))$p.value,
                              groups_corr = abs(cor.test(Groups, lag(Groups, n = i))$estimate),
                              groups_p = cor.test(Groups, lag(Groups, n = i))$p.value,
                              area_corr = abs(cor.test(Area, lag(Area, n = i))$estimate),
                              area_p = cor.test(Area, lag(Area, n = i))$p.value,
                              height_corr = abs(cor.test(School_Height, lag(School_Height, n = i))$estimate),
                              height_p = cor.test(School_Height, lag(School_Height, n = i))$p.value,
                              lag = i)

>>>>

  new_autocorrs <- school_data_no_removals %>% group_by(Date_Trial) %>%
                    filter(!Date_Trial %in% c("2021_3_25_30","2020_7_28_29","2021_10_6_34",
                                              "2021_7_7_16","2021_3_25_7","2021_3_25_22",
                                              "2021_8_3_8")) %>%
                    summarise(nnd_corr = abs(cor.test(NND, lag(NND, n = i))$estimate),
                              nnd_p = cor.test(NND, lag(NND, n = i))$p.value,
                              polar_corr = abs(cor.test(School_Polar, lag(School_Polar, n = i))$estimate),
                              polar_p = cor.test(School_Polar, lag(School_Polar, n = i))$p.value,
                              speed_corr = abs(cor.test(School_Speed, lag(School_Speed, n = i))$estimate),
                              speed_p = cor.test(School_Speed, lag(School_Speed, n = i))$p.value,
                              groups_corr = abs(cor.test(Groups, lag(Groups, n = i))$estimate),
                              groups_p = cor.test(Groups, lag(Groups, n = i))$p.value,
                              area_corr = abs(cor.test(Area, lag(Area, n = i))$estimate),
                              area_p = cor.test(Area, lag(Area, n = i))$p.value,
                              height_corr = abs(cor.test(School_Height, lag(School_Height, n = i))$estimate),
                              height_p = cor.test(School_Height, lag(School_Height, n = i))$p.value,
                              lag = i)

### 2023-07-20 Fish Data Analysis/Results_Text.qmd
Reverting to old files, fixing 3d matching errors
Adding more calibrations

glmm_school_stats_table <- tibble(Stat = c(rep("NND",4),rep("Height",4),rep("Polarization",4),rep("Speed",4),rep("Area",4),rep("Groups",4)),
       Flow_or_Still = rep( c(rep("Still",2) , rep("Flow",2)), 6),
       Condition = rep(c("Ablation","Darkness"), 12),
       DF = rep(c(rep(length(nnd_glmer_still@resp$y)-3,2),
                  rep(length(nnd_glmer_flow@resp$y)-3,2)),times = 6),
       Chisq = c(nnd_s_aov_me$Chisq[1:2],nnd_f_aov_me$Chisq[1:2],
                 height_s_aov_me$Chisq[1:2],height_f_aov_me$Chisq[1:2],
                 polar_s_aov_me$Chisq[1:2],polar_f_aov_me$Chisq[1:2],
                 speed_s_aov_me$Chisq[1:2],speed_f_aov_me$Chisq[1:2],
                 area_s_aov_me$Chisq[1:2],area_f_aov_me$Chisq[1:2],
                 groups_s_aov_me$Chisq[1:2],groups_f_aov_me$Chisq[1:2]),

       P_Val = c(nnd_s_aov_me$`Pr(>Chisq)`[1:2],nnd_f_aov_me$`Pr(>Chisq)`[1:2],
                 height_s_aov_me$`Pr(>Chisq)`[1:2],height_f_aov_me$`Pr(>Chisq)`[1:2],
                 polar_s_aov_me$`Pr(>Chisq)`[1:2],polar_f_aov_me$`Pr(>Chisq)`[1:2],
                 speed_s_aov_me$`Pr(>Chisq)`[1:2],speed_f_aov_me$`Pr(>Chisq)`[1:2],
                 area_s_aov_me$`Pr(>Chisq)`[1:2],area_f_aov_me$`Pr(>Chisq)`[1:2],
                 groups_s_aov_me$`Pr(>Chisq)`[1:2],groups_f_aov_me$`Pr(>Chisq)`[1:2]),

@@

turning_results <- tibble(Flow_or_Still = c("Still","Still","Still","Still","Still","Flow","Flow","Flow","Flow","Flow"),
       Factor = c("FNR","Ablation","Darkness","FNR:Ablation","FNR:Darkness",
                  "FNR","Ablation","Darkness","FNR:Ablation","FNR:Darkness"),
       DF = c(rep(length(turning_glm_still$y)-3,5),rep(length(turning_glm_flow$y)-3,5)),
       LR_Chisq = c(tgs_aov$`LR Chisq`,tgf_aov$`LR Chisq`),
       P_Val = c(tgs_aov$`Pr(>Chisq)`,tgf_aov$`Pr(>Chisq)`),
       Is_Sig = P_Val < 0.05)

@@

single_vs_eight_results <- tibble(Condition = c("Light","Light","Ablated","Ablated","Darkness","Darkness"),
       Factor = c("Type","FNR:Type","Type","FNR:Type","Type","FNR:Type"),
       DF = c(rep(length(light_turning_glm$y)-3,2),rep(length(ablated_turning_glm$y)-3,2),rep(length(dark_turning_glm$y)-3,2)),
       LR_Chisq = c(ltg_aov$`LR Chisq`[2:3],altg_aov$`LR Chisq`[2:3],dtg_aov$`LR Chisq`[2:3]),
       P_Val = c(ltg_aov$`Pr(>Chisq)`[2:3],altg_aov$`Pr(>Chisq)`[2:3],dtg_aov$`Pr(>Chisq)`[2:3]),
       Is_Sig = P_Val < 0.05)

>>>>

glmm_school_stats_table <- tibble(Stat = c(rep("NND",4),rep("Height",4),rep("Polarization",4),rep("Speed",4),rep("Area",4),rep("Groups",4)),
       Flow_or_Still = rep( c(rep("Still",2) , rep("Flow",2)), 6),
       Condition = rep(c("Ablation","Darkness"), 12),
       DF = rep(c(rep(length(nnd_glmer_still@resp$y)-3,2),
                  rep(length(nnd_glmer_flow@resp$y)-3,2)),times = 6),
       Chisq = round(c(nnd_s_aov_me$Chisq[1:2],nnd_f_aov_me$Chisq[1:2],
                 height_s_aov_me$Chisq[1:2],height_f_aov_me$Chisq[1:2],
                 polar_s_aov_me$Chisq[1:2],polar_f_aov_me$Chisq[1:2],
                 speed_s_aov_me$Chisq[1:2],speed_f_aov_me$Chisq[1:2],
                 area_s_aov_me$Chisq[1:2],area_f_aov_me$Chisq[1:2],
                 groups_s_aov_me$Chisq[1:2],groups_f_aov_me$Chisq[1:2]),2),

       P_Val = round(c(nnd_s_aov_me$`Pr(>Chisq)`[1:2],nnd_f_aov_me$`Pr(>Chisq)`[1:2],
                 height_s_aov_me$`Pr(>Chisq)`[1:2],height_f_aov_me$`Pr(>Chisq)`[1:2],
                 polar_s_aov_me$`Pr(>Chisq)`[1:2],polar_f_aov_me$`Pr(>Chisq)`[1:2],
                 speed_s_aov_me$`Pr(>Chisq)`[1:2],speed_f_aov_me$`Pr(>Chisq)`[1:2],
                 area_s_aov_me$`Pr(>Chisq)`[1:2],area_f_aov_me$`Pr(>Chisq)`[1:2],
                 groups_s_aov_me$`Pr(>Chisq)`[1:2],groups_f_aov_me$`Pr(>Chisq)`[1:2]),2),

@@

turning_results <- tibble(Flow_or_Still = c("Still","Still","Still","Still","Still","Flow","Flow","Flow","Flow","Flow"),
       Factor = c("FNR","Ablation","Darkness","FNR:Ablation","FNR:Darkness",
                  "FNR","Ablation","Darkness","FNR:Ablation","FNR:Darkness"),
       DF = c(rep(length(turning_glm_still$y)-3,5),rep(length(turning_glm_flow$y)-3,5)),
       LR_Chisq = round(c(tgs_aov$`LR Chisq`,tgf_aov$`LR Chisq`),2),
       P_Val = round(c(tgs_aov$`Pr(>Chisq)`,tgf_aov$`Pr(>Chisq)`),2),
       Is_Sig = P_Val < 0.05)

@@

single_vs_eight_results <- tibble(Condition = c("Light","Light","Ablated","Ablated","Darkness","Darkness"),
       Factor = c("Type","FNR:Type","Type","FNR:Type","Type","FNR:Type"),
       DF = c(rep(length(light_turning_glm$y)-3,2),rep(length(ablated_turning_glm$y)-3,2),rep(length(dark_turning_glm$y)-3,2)),
       LR_Chisq = round(c(ltg_aov$`LR Chisq`[2:3],altg_aov$`LR Chisq`[2:3],dtg_aov$`LR Chisq`[2:3]),3),
       P_Val = round(c(ltg_aov$`Pr(>Chisq)`[2:3],altg_aov$`Pr(>Chisq)`[2:3],dtg_aov$`Pr(>Chisq)`[2:3]),3),
       Is_Sig = P_Val < 0.05)
